How has the Brazilian Amazon been constructed as a problem? Presidential speeches and transnational politics since 1985

### 2023-01-30 Submission/Re-submission/draft/draft_resubmission.rmd
Updated location categories and added all mixed-types to both plots and regression as a separate, but encompassing, category

```{=latex}
\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
```
```{=latex}
\wordcount{ 7685 (including abstract, text, references, and footnotes)}
```
```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(modelsummary)
library(plm)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
  select(-location_cat) %>%
  distinct()
ama <- left_join(ama, location_km, by = "location")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year_lag <- amazon_def_year
# missing years are missed with first non missing value
adr <- data.frame(year = c(1985, 1986, 1987), 
                  def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                  def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data 
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))
# Prepare data for problem-constructions
sov <- ama %>% 
  filter(sov==1) %>% 
  count(sov, year) %>%
  group_by(year) %>%
  select(-c(sov))%>%
  rename (sov = n)
ei <- ama %>% 
  filter(ei==1) %>% 
  count(ei, year) %>%
  group_by(year) %>%
  select(-c(ei))%>%
  rename (ei = n) %>%
  ungroup() %>%
  tibble::add_row(year = 2017, ei = 0) %>%
  tibble::add_row(year = 2018, ei = 0)
sd <- ama %>% 
  filter(sd==1) %>% 
  count(sd, year) %>%
  group_by(year) %>%
  select(-c(sd))%>%
  rename (sd = n)
con <- ama %>% 
  filter(con==1) %>% 
  count(con, year) %>%
  group_by(year) %>%
  select(-c(con))%>%
  rename (con = n)
other <- ama %>% 
  filter(other==1) %>% 
  count(other, year) %>%
  group_by(year) %>%
  select(-c(other))%>%
  rename (other = n)
temp <- ei %>% 
  left_join(other) %>% 
  left_join(con) %>% 
  left_join(sd) %>% 
  left_join(sov) %>% 
  replace(is.na(.), 0)
# Get mixed types in
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ "Pure National Sovereignty",
                                   mixed_type == '0_1_0_0' ~ "Pure Economic Integration", 
                                   mixed_type == '0_0_1_0' ~ "Pure Social Development",
                                   mixed_type == '0_0_0_1' ~ "Pure Environmental Conservation",
                                   mixed_type == '0_0_0_0' ~ "Other",
                                   mixed_type == '0_1_0_1' ~ "Economic Conservation",
                                   mixed_type == '0_1_1_0' ~ "Social Economic",
                                   mixed_type == '1_0_0_1' ~ "Sovereign Conservation",
                                   mixed_type == '0_1_1_1' ~ "Economic, Social,\nand Conservation",
                                   mixed_type == '1_1_0_0' ~ "Economic Sovereignty",
                                   mixed_type == '0_0_1_1' ~ "Social Conservation",
                                   grepl("1_0_1_0|1_0_1_0|1_0_1_1|1_1_0_1|1_1_1_0|1_1_1_1",
                                         mixed_type) ~ "Other Mixed-types"),
         levels = c("Pure Economic Integration", "Pure Environmental Conservation",
                    "Pure Social Development",
                    "Pure National Sovereignty", "Other", "Economic Conservation", 
                    "Social Economic", "Sovereign Conservation",
                    "Economic, Social,\nand Conservation",
                    "Economic Sovereignty", "Social Conservation", "Other Mixed-types")),
         mx_cat2 = case_when(grepl("Pure Economic Integration|Pure Environmental Conservation|
                                   |Pure Social Development|Pure National Sovereignty",
                                   mx_cat) ~ "Pure-types",
                             grepl("^Other$", mx_cat) ~ "Other",
                             grepl("Economic Conservation|Social Economic|Sovereign Conservation|
                                   |Economic, Social,\nand Conservation|Economic Sovereignty|
                                   |Social Conservation|Other Mixed-types",
                                   mx_cat) ~ "Mixed-types"),
        election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
        peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
        # py_1989=ifelse(grepl("1989", year), 1, 0),
        # py_1992=ifelse(grepl("1992", year), 1, 0),
        # py_2009=ifelse(grepl("2009", year), 1, 0),
        # py_2015=ifelse(grepl("2015", year), 1, 0),
        # py_2019=ifelse(grepl("2019", year), 1, 0),
         location_cat = factor(location_cat,
                               levels = c("Amazonian States",
                                          "Non Amazonian States",
                                          "Brasilia",
                                          "Amazonian Countries",
                                          "International")))

ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0))
```

@@

## Count average words in Amazonian Statements
# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
## 131 on average

@@

```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  geom_line(aes(y=mean(perc)), color="black", linewidth=.5, linetype="dotted")+
  scale_y_continuous(labels = percent_format()) + 
  annotate("text", x = 1985, y = 0.18, label = "15.4%", size = 3.5)+
  annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
  annotate("text", x = 1992.5, y = 0.26, label = "Earth Summit", size = 3)+
  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
  annotate("text", x = 2022, y = 0.225, label = "Murder\nof Bruno\nand Dom", size = 3)+
  labs(x = "", y = "",
       title = "Share of speeches that mention the Amazon per year",
       subtitle = "Sample composed by all 6130 speeches since 1985",
       color='Y series') +
  theme_am()
```

@@

```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am()+
  theme(legend.position = "bottom")
```

@@

Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon. Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem. Constructing the Amazon as multiple issues averages at 18% of all constructions over time. Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence. Figure 4, below, displays the averages of mixed-types constructions by presidents.

```{r Figure mixed, fig.cap="Mixed-types by president", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
ama_mx %>%
  count(president, mx_cat, mx_cat2) %>%
  group_by(president) %>%
  mutate(perc = n / sum(n)) %>%
  filter(mx_cat2 == "Mixed-types") %>%
  mutate(president = factor(president, levels = c("Sarney", "Collor", "Itamar", "FHC",
                                                  "Lula", "Dilma", "Temer", "Bolsonaro"))) %>%
  ggplot(aes(x = president, y = perc, fill = mx_cat,
             label = scales::percent(perc, accuracy=.1))) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(size = 2, position = position_stack(vjust = .5)) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_brewer(type = "qual", palette = "Set2", direction= 1) +
  labs(x = "", y = "", title ="Share of each mixed-type problem-constructions by president",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "") +
  theme_am() +
  theme(legend.position = "right")
```

Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation. This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time. This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.Mixed-types are particular interesting considering both Lula and Bolsonaro, who construct the Amazon as a multifaceted issue more frequently than other presidents. Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990].

@@

# model 3
c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small",
                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
                                             "Social Development", "National Sovereignty", "Amazonian   Speech"),
                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Deforestation", "Inflation", "Election Year", "High-profile Events"))
```

@@

```{r setting vs outcome, fig.cap="Problem-constructions, settings, and policy outcomes", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
amazon_def_year <- amazon_def_year%>%
  mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
ama_mx %>%
  count(mx_cat, location_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(location_cat == "Amazonian States"|
           location_cat == "International",
         mx_cat == "Pure Economic Integration"|
           mx_cat == "Pure Environmental Conservation") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color=mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+
  facet_wrap(~location_cat+mx_cat)+
  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
       caption = "Curves in the plot were smoothed using loess method.")+
  theme_am()+
  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/120,fill=extremes),alpha=.5)+
  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
  annotate("text", x = 2009, y = 0.20, label = "27'772 km2\ndeforested" , size = 1.5, color="darkolivegreen", face="bold")+
  annotate("text", x = 2015, y = 0.038, label = "4'571 km2\ndeforested", size = 1.5, color="darkolivegreen", face="bold")
```

>>>>

```{=latex}
\keywords{ discourse analysis, transnational governance, environmental policy, Brazilian Amazon, supervised learning, deforestation}
```

```{=latex}
\wordcount{ 7685 (including abstract, text, references, and footnotes)}
```

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(dplyr)
library(tidyr)
library(scales)
library(RColorBrewer)
library(stargazer)
library(kableExtra)
library(tibble)
library(readxl)
library(ggplot2)
library(gridExtra)
library(modelsummary)
library(plm)
Sys.setlocale("LC_ALL", "C")
options(stringsAsFactors = FALSE, scipen = 999)
```

@@

```{r data, message=FALSE, warning=FALSE, include=FALSE}
# Load data
pop <- readRDS("~/Documents/GitHub/amazondef/Replication_files/BR_presid_speeches_final.Rds")
ama <- readRDS("~/Documents/GitHub/amazondef/Replication_files/final_data_as.Rds")
ama <- ama %>% select(-c(title, date, text, false_positives)) %>% rename (ei= "EI", sd= "SD")
AAI <- readRDS("~/Documents/GitHub/amazondef/Replication_files//AAI.Rds")
location_km <- read_excel("~/Documents/GitHub/amazondef/Replication_Files/location_km.xlsx") %>%
  select(-location_cat) %>%
  distinct()
ama <- left_join(ama, location_km, by = "location")
amazon_def_year <- readRDS("~/Documents/GitHub/amazondef/Replication_files//amazon_def_year.Rds")
amazon_def_year_lag <- amazon_def_year
# missing years are missed with first non missing value
adr <- data.frame(year = c(1985, 1986, 1987), 
                  def_year = c(21.050, 21.050, 21.050))
amazon_def_year <- rbind(adr, amazon_def_year) # Missing year data 
amazon_def_year_lag$year <- amazon_def_year_lag$year + 1
adr <- data.frame(year = c(1985, 1986, 1987, 1988),
                  def_year = c(21.050, 21.050, 21.050, 21.050))
amazon_def_year_lag <- rbind(adr, amazon_def_year_lag) # Missing year data 
hp = data.frame(beg = c(1985, 1990, 1993, 1994, 2002, 2010, 2016, 2018),
                end = c(1990, 1993, 1994, 2002, 2010, 2016, 2018, 2022),
                label = c(1987, 1991, 1993, 1998, 2006, 2013, 2017, 2020),
                presid = c("Sarney", "Collor", "Franco", "Cardoso", "Lula",
                           "Rousseff", "Temer", "Bolsonaro"))

# Get PC in
ama_mx <-  ama %>%
  unite(mixed_type, sov:con, sep="_") %>%
  mutate(mx_cat = factor(case_when(mixed_type == '1_0_0_0' ~ 
                                     "Pure National Sovereignty",
                                   mixed_type == '0_1_0_0' ~ 
                                     "Pure Economic Integration", 
                                   mixed_type == '0_0_1_0' ~ 
                                     "Pure Social Development",
                                   mixed_type == '0_0_0_1' ~ 
                                     "Pure Environmental Conservation",
                                   mixed_type == '0_0_0_0' ~ 
                                     "Other",
                                   TRUE ~ "Mixed-types"),
         levels = c("Pure Economic Integration",
                    "Pure Environmental Conservation",
                    "Pure Social Development",
                    "Pure National Sovereignty",
                    "Other", "Mixed-types")),
        election_year = ifelse(grepl("1989|1994|1998|2002|2006|2010|2014|2018",
                                      year), 1, 0),
        peak_year = ifelse(grepl("1989|1992|2009|2019|2022", year), 1, 0),
        location_cat = factor(case_when(location_cat == "International" ~ 
                                          "Non Amazonian Countries",
                                        location_cat == 
                                          "Amazonian States" ~ 
                                          "Amazonian States",
                                        location_cat == "Amazonian Countries" ~ 
                                          "Amazonian Countries",
                                        TRUE ~ "Non Amazonian States"),
                              levels = c("Amazonian States",
                                         "Non Amazonian States",
                                         "Amazonian Countries",
                                         "Non Amazonian Countries")))

ama_model_lag <- dplyr::left_join(ama_mx, amazon_def_year_lag, by = "year") %>%
dplyr::left_join(AAI, by = "year") %>%
filter(location_cat != "Non Identified") %>%
  mutate(con_vs_all = ifelse(mx_cat == "Pure Environmental Conservation", 1, 0),
         EI_vs_all = ifelse(mx_cat == "Pure Economic Integration", 1, 0),
         SD_vs_all = ifelse(mx_cat == "Pure Social Development", 1, 0),
         sov_vs_all = ifelse(mx_cat == "Pure National Sovereignty", 1, 0),
         mixed_vs_all = ifelse(mx_cat == "Mixed-types", 1, 0))
```

@@

## Count average words in Amazonian Statements
## Need to use original text data
# amazon_speeches_long <- readRDS("~/Documents/GitHub/amazondef/Replication_Files/amazon_speeches_long.Rds")
# sum(stringr::str_count(amazon_speeches_long$AM2, '\\w+'))/2048
## 131 on average

@@

```{r Figure speeches, fig.cap="Amazonian speeches in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE, include=TRUE}
perc1 <- pop %>%
  count(amazon_speech, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>%
  filter(amazon_speech == 1) %>% 
  select(c(perc, amazon_speech, year))
perc1 %>% ggplot(., aes(x = year, y = perc)) +
  geom_line(color = "darkgreen") +
  geom_line(aes(y=mean(perc)), color="black", linewidth=.5, linetype="dotted")+
  scale_y_continuous(labels = percent_format()) + 
  annotate("text", x = 1985, y = 0.165, label = "15.4%", size = 3.5)+
  annotate("text", x = 1988.7, y = 0.345, label = "Murder of\nChico Mendes", size = 3)+
  annotate("text", x = 1992.5, y = 0.26, label = "Earth Summit", size = 3)+
  annotate("text", x = 2009, y = 0.24, label = "Copenhagen Summit", size = 3)+
  annotate("text", x = 2019, y = 0.26, label = "2019 Record\nAugust Fires", size=3) +
  annotate("text", x = 2022, y = 0.225, label = "Murder\nof Bruno\nand Dom", size = 3)+
  labs(x = "", y = "",
       title = "Share of speeches that mention the Amazon per year",
       subtitle = "Sample composed by all 6130 speeches since 1985",
       color='Y series') +
  theme_am()
```

@@

```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
summary(as.factor(ama_mx$mx_cat))
ama_mx %>%
  count(mx_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat != "Other") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am()+
  theme(legend.position = "bottom")
```

@@

<!-- Finally, our operationalization foresees the possibility of presidents might mixing multiple problem-constructions within a same statement about the Amazon. Mixed-type problem-constructions in discourse offer more intricate understandings of the Amazon as a problem. Constructing the Amazon as multiple issues averages at 18% of all constructions over time. Some mixed-types rarely appear so we focus our discussion on those mixed-types with higher incidence. Figure 4, below, displays the averages of mixed-types constructions by presidents.Overall, there is a general increase of mixed-types over time, which is expected given the rise of global agendas understanding interconnections of social, environmental, and economic domains such as the Millennium Development Goals and the Sustainable Development Goals.The most frequent mixed-type problem construction of the Amazon is economic conservation. This mixed-type construction, composed of Amazonian statements that construct the Amazon as a problem of both economic integration and environmental conservation, generally increased over time. This increase suggests that later presidents, along with being more diverse in how they construct the Amazon as an issue, increasingly find ways to reconcile the dictum between the economy and the environment that had prevailed in the previous years.Mixed-types are particular interesting considering both Lula and Bolsonaro, who construct the Amazon as a multifaceted issue more frequently than other presidents. Lula usually mixed economic integration with environmental conservation and social development when constructing the Amazon as an issue, while Bolsonaro constructs the Amazon as an issue of national sovereignty and economic integration much more than any other president, mimicking the military dictatorship discourses and policies toward the region [@hecht1990]. -->

@@

# model 3
c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")
c5 <- plm(mixed_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + peak_year,
                         data = ama_model_lag,
                         model = "within", index = "president")

stargazer::stargazer(c1, c2, c3, c4, c5, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small",
                      dep.var.labels = c("Environmental Conservation",
                                         "Economic Integration",
                                         "Social Development",
                                         "National Sovereignty",
                                         "Mixed-types"),
                     covariate.labels = c("Non Amazonian States",
                                          "Amazonian Countries",
                                          "Non Amazonian Countries",
                                          "Deforestation",
                                          "Inflation",
                                          "Election Year",
                                          "High-profile Events"))
```

@@

```{r setting vs outcome, fig.cap="Problem-constructions, settings, and policy outcomes", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
amazon_def_year <- amazon_def_year %>%
  mutate(extremes= ifelse(year == 2004|year == 2012, "yes","no"))
ama_mx %>%
  count(mx_cat, location_cat, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(location_cat == "Amazonian States"|
           location_cat == "Non Amazonian Countries",
         mx_cat == "Pure Economic Integration"|
           mx_cat == "Pure Environmental Conservation") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color=mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1))+
  facet_wrap(~location_cat+mx_cat)+
  labs(x = "", y = "", title ="Relationship between problem-constructions and deforestation rates",
       subtitle = "Bars indicated yearly deforestation level and curves indicated yearly share of problem-construction.",
       caption = "Curves in the plot were smoothed using loess method.")+
  theme_am()+
  geom_col(amazon_def_year, mapping = aes(x = year, y = def_year/120,fill=extremes),alpha=.5)+
  scale_fill_manual(values=c("lightgrey", "darkolivegreen"))+
  annotate("text", x = 2009, y = 0.20, label = "27'772 km2\ndeforested" , size = 1.5, color="darkolivegreen", face="bold")+
  annotate("text", x = 2015, y = 0.038, label = "4'571 km2\ndeforested", size = 1.5, color="darkolivegreen", face="bold")
```
